Paper reviews

### 2015-05-02 Rmarkdown/paper_review.Rmd
typo

The raw $\beta$-values are weighted according to the binomial likelihood and a tricube kernel. The binomial likelihood weights points inversely to their standard error, $se(\beta_{i, j})$, and the tricube kernal gives greater weight to those $\beta_{i, j}$ near the centre of the window.

>>>>

The raw $\beta$-values are weighted according to the binomial likelihood and a tricube kernel. The binomial likelihood weights points inversely to their standard error, $se(\beta_{i, j})$, and the tricube kernel gives greater weight to those $\beta_{i, j}$ near the centre of the window.
